Reasoning About a Machine with Local Capabilities

### 2018-05-11 toplas/paper.tex
Added a paragraph outlining the new additions in this paper.

>>>>

\begin{toplas}
  This paper is an extension of a published conference
  paper\citep[Skorstengaard:esop2018]. We have made minor improvements to
  readability and completeness throughout the paper, but we highlight the
  following changes:
  \begin{itemize}
  \item We have added an introduction to the \sectionname~\nameref{sec:logical-relation} that provide informal intuition about how the logical relation machinery comes into play in this setting.
  \item We have added a proof sketch for the \nameref{thm:ftlr} and one for Lemma~\ref{lem:correctness-g1}, the correctness lemma for the awkward example.
  \item We have added a section on malloc.
    In particular, we provide the specification for malloc used in the examples of the paper.
  \item We have added a section on macro instructions.
    All the macro instructions are described and the implementation of \texttt{scall} is provided.
  \item We have added a section on reasoning about programs that run on a capability machine.
  \item We have added many details previously found only in the technical appendix~\citep{technical_appendix} to the paper.
    Many of the details we did not include in the paper are now in the appendix of the paper.
  \end{itemize}
\end{toplas}
